---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    logo: 
    theme: flatly
    social: [ "linkedin", "facebook", "twitter", "menu" ]
    source_code: "https://github.com/eddychetz/web-apps-with-rshiny-flexdashboard.git"
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(rpivotTable) # for pivotal tables
library(DT) # for data tables
library(ggplot2)
library(plotly)
library(correlationfunnel)
library(tidyquant)
library(tidyverse)
library(openintro) # deal with abbreviations
library(highcharter) # maps
library(ggvis) # visualization
library(rpart) # partition and pre-processing
library(caret) # Regression and classification
library(dummy) # convert factor to dummy vars

library(janitor) # Clean names
library(tidymodels) # Modeling

churn_tbl <- read_csv("./data/customer_churn.csv")

mycolors <- c("blue", "#FFC125", "darkgreen", "darkorange")

# DATA ----
customer_churn_tbl <- churn_tbl %>%
    # Clean names
    clean_names()%>%
    # Casting categorical columns
    mutate_if(is.character, as_factor)
customer_churn_tbl%>%glimpse()

# MODEL ----

# pre-processing pipeline
recipe_spec <- recipe(churn ~ ., 
                      data = customer_churn_tbl) %>%
    # Remove irrelevant columns
    step_rm(customer_id) %>%
    # Encode cat features
    step_dummy(all_nominal_predictors(), 
               one_hot = TRUE)

recipe_spec %>% 
    prep() %>% 
    bake(customer_churn_tbl)

# model specification
model_spec <- rand_forest(
    trees = 200, 
    min_n = 5)%>%  
    set_mode("classification")%>%
    set_engine("randomForest")

# Model training pipeline
wflw_fit_rf <- workflow() %>%
    add_recipe(recipe_spec) %>%
    add_model(model_spec) %>%
    fit(customer_churn_tbl)

# Class prediction
wflw_fit_rf %>% 
    predict(customer_churn_tbl)


pred_prob <- wflw_fit_rf %>%
    predict(customer_churn_tbl, type = "prob")

# Testing the function
pred <- wflw_fit_rf %>%
    predict(customer_churn_tbl)

# Model evaluation
churn_tab <- table(customer_churn_tbl$churn, pred$.pred_class)

cm <- confusionMatrix(churn_tab, mode = "prec_recall")

#EXPLAINER

# Custom prediction function
pred_func <- function(model, newdata) {
    predict(model, 
            newdata, 
            type = "prob"
            ) %>% 
        pull(2)
}
explain_rf <- DALEX::explain(
    model            = wflw_fit_rf,
    data             = customer_churn_tbl %>% select(-churn),
    y                = as.numeric(customer_churn_tbl$churn),
    predict_function = pred_func,
    label            = "Random Forest"
)
```

Interactive Data Visualization {data-icon="fa-signal"}
=======================================================

Row {data-height="100" .sidebar}
----------------------------------------

#### **Customer Churn**

* Customer churn varies significantly by __contract type__.

* A potential strategy is to encourage purchasing long-term contracts versus month-to-month. 

```{r}
shiny::sliderInput("n_breaks", label = "Numeric Features:",
              min = 2, max = 8, value = 4, step = 1)
```

```{r}

shiny::selectInput("chart_type", label = "Chart Type:", 
                     choices = c("Aggregated", "Customer-Level"))

```

Row {data-height="650"}
------------------------------


```{r}
# data("USArrests", package = "datasets")
# data("usgeojson")
# 
# USArrests <- mutate(USArrests, state = rownames(USArrests))
# 
# p1 <- highchart() %>%
#   hc_title(text = "Violent Crime Rates by US State") %>%
#   hc_subtitle(text = "Source: USArrests data") %>%
#   hc_add_series_map(usgeojson, USArrests,
#     name = "Murder arrests (per 100,000)",
#     value = "Murder", joinBy = c("woename", "state"),
#     dataLabels = list(
#       enabled = TRUE,
#       format = "{point.properties.postalcode}"
#     )
#   ) %>%
#   hc_colorAxis(stops = color_stops()) %>%
#   hc_legend(valueDecimals = 0, valueSuffix = "%") %>%
#   hc_mapNavigation(enabled = TRUE)
# p1
```

### **Feature Importance**

```{r}
output$g1 <- renderPlot({
   customer_churn_tbl %>%
    select(-customer_id) %>%
    # #mutate(TotalCharges = ifelse(is.na(TotalCharges), 0, TotalCharges)) %>%
    # replace_na(replace = list(TotalCharges = 0)) %>%
    # binarize(n_bins = input$n_breaks,
    #          thresh_infreq = 0.05, 
    #          one_hot = F) %>%
    #     
    # correlate(target = churn__Yes) %>%
    #     
    # plot_correlation_funnel(interactive = T) +
    # geom_point(size = 3, alpha = 0.7, color = palette_light()[1])
    binarize(n_bins = input$n_breaks) %>%
    correlate(churn__Yes) %>%
    plot_correlation_funnel()

})
plotOutput("g1", height = "80%")
br()
```

### **Contract Type Effect**

```{r}

output$p1 <- renderPlotly({
  
  if (input$chart_type == "Aggregated") {
    g <- customer_churn_tbl %>%
      select(contract, churn) %>%
      count(contract, churn) %>%
      group_by(contract) %>%
      mutate(prop = n / sum(n)) %>%
      ungroup() %>%
      mutate(contract = as_factor(contract) %>% fct_reorder(prop) %>% fct_rev()) %>%
      filter(churn == 'Yes') %>%
      ggplot(aes(prop, contract)) +
      geom_col(aes(text = str_glue("Churn %: {scales::percent(prop)}")), 
               fill = palette_light()[1]) +
      scale_x_continuous(labels = scales::percent_format()) +
      theme_tq() 
  } else {
    g <- customer_churn_tbl %>%
      mutate(value = ifelse(churn == 'Yes', 1, 0)) %>%
      mutate(contract = factor(contract, 
                               levels = c("Month-to-month", "One year", "Two year"))) %>%
      ggplot(aes(value, contract, color = churn)) +
      geom_jitter((aes(text = str_glue({
        "Customer ID: {customer_id}
        Contract: {contract}
        Tenure: {tenure}"
      }))), 
                  alpha = 0.5) +
      scale_color_tq() +
      scale_x_continuous(breaks = c(0,1)) +
      theme_gray() +
      labs(x = "Churn Numeric (Yes = 1, No = 0)")
  }
  
   ggplotly(g)
})
plotlyOutput("p1", height = "80%")
```

<!-- Row {data-height=50} -->
<!-- ------------------------------ -->
<!-- **Hello* -->


Data Table {data-icon="fa-table"}
==============================================

```{r}
datatable(churn_tbl,
          caption = T,
          filter = "top",
          options = list(pageLength = 10))
```

Pivot Table {data-icon="fa-solid fa-table-pivot"}
================================================

```{r}
rpivotTable(churn_tbl[,2:5],
            aggregatorName = "Count",
            cols = "Contract",
            rows = "Churn",
            rendererName = "Heatmap")

```

Data Analysis {data-icon="fa-magnifying-glass-chart"}
================================================

Row {data-height=250, .sidebar}
-----------------------

**Model Parameters**

```{r}
shiny::selectInput("model_type", label = "Model Selection:", 
                     choices = c("Random Forest", "XGBoost"))
```

Row {data-height=250}
-----------------------

### Model Accuracy

```{r}

renderValueBox({
    #churn <- filter(churn_tbl, gender == "Male")
    valueBox(paste(round(cm$overall[1]*100, digits = 2), "%"), 
         icon = "fa-user")
})
```

### Precision

```{r}
renderValueBox({
    #churn <- filter(churn_tbl, gender == "Male")
    valueBox(paste(round(cm$byClass[5]*100, digits = 2), "%"), 
         icon = "fa-user")
})
```

### Recall

```{r}
renderValueBox({
    #churn <- filter(churn_tbl, gender == "Male")
    valueBox(paste(round(cm$byClass[6]*100, digits = 2), "%"), 
         icon = "fa-user")
})
```


Row {data-height="250"}
-----------------------
```{r}
# EXPLAINABLE AI REPORT ----

# Custom prediction function
pred_func <- function(model, newdata) {
    predict(model, 
            newdata, 
            type = "prob"
            ) %>% 
        pull(2)
}

# Information to display
output$p3 <- renderTable({
    
        tabl <- DALEX::model_performance(explain_rf)
        tabl$measures
})
tableOutput("p3")
```

Row {data-height="650"}
------------------------------

### Hello classification model


Summary {data-orientation=columns}
================================================

```{r}
# gauge(round((1-(churn_tbl%>%
#                     select(contains("month"))%>%
#                     sum(churn_tbl$Churn == "Yes")/length(churn_tbl$Churn)))*100, 
#             digits = 1),
#             min = 0,
#             max = 100,
#       symbol = "%",
#             gaugeSectors(success = c(0, 25),
#                          warning = c(25, 70),
#                          danger = c(70, 100),
#                          colors = c("green", "yellow", "red")))
```

**Report**

* This is a report on `r length(churn_tbl$tenure)` customers.


 **Problem**

* Customer Churn is impacting revenue sales. What can we do?


 **Solution**


* Customer churn varies significantly by __contract type__.

* A potential strategy is to encourage purchasing long-term contracts versus month-to-month. 

* My analysis suggests that we can __reduce churn by moving customers to longer term contracts.__


This report was generated on `r Sys.Date()`.

About {data-icon="fa-user"}
=============================

**Created by:** Data Scientist, [Eddwin Cheteni](https://mlaihub.netlify.app/)

**Confidential:** HIGHLY!